An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
Plaatje CSDF

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{cite}
\usepackage[cmex10]{amsmath}

@@

  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{cite}
\usepackage[cmex10]{amsmath}
\usetikzlibrary{calc,positioning}

@@

  Functional specifications of computations can be represented by CSDF graphs using a straightforward translation.
  As an example, consider the functional specification of a simple dot product of two vectors, written in the functional programming language Haskell.

dot\_product xs ys = fold (+) 0 (zipWith (*) xs ys)\todo{Use nice listing environment}

  The CSDF graph representation of this specification is depicted in Figure~\ref{fig:csdf-dotproduct}.
  \begin{figure}[h!]
    \centering
    \input{csdf-dp}
    \caption{Cyclo-static dataflow graph representation of dot-product}
    \label{fig:csdf-dotproduct}
  \end{figure}
